CloneOverflow: \\ Discovery of Online Code Clones between \\Stackoverflow and Open Source Projects

### 2016-10-21 latex-acm/cloneoverflow.tex
Updates

\section{Introduction}
\begin{itemize}
	\item Definition of code clones, online code clones, pros \& cons
	\item Problems of code reuse (bug propagation, licensing conflicts)
	\item Roles of Q\&A websites in supporting software development and education
\end{itemize}

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We processed 130,644,707 clone pairs and manually investigated 2,371 clone pairs between Java code fragments obtained from Stackoverflow accepted answers and 63 Java open source projects.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and online Q\&A websites:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license. Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.

\section{Research Questions}
The study aims to answer the following research questions: \\ 
\textbf{RQ1 (online code clone):} \textit{To what extent  source code is reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale. \newline
\textbf{RQ2 (flow of online code clone):} \textit{what are the directions that source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied. Is it from Q\&A site to open source projects, or the other way around, or both? \newline
\textbf{RQ3 (classification of online code clone):} \textit{How do the online code clones happen?} What are the major causes creating the online code clones? \newline
\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?

\section{Experimental Setup}

\subsection{Dataset}
In our study, we selected the latest version of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects. \textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects. The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.

\subsection{Clone Detectors}
We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}

\subsection{Agreement-based Clone Detection}
We adopted an idea of clone agreement normally used in clone research \cite{Wang2013,Funaro2010}.

>>>>

\section{Introduction}
Code cloning is an activity of reusing source code by copy and paste. It normally occurs in software development and account from 7\% to 23\% in typical software systems \cite{Bellon2007}. The benefits and drawbacks of clones are still controversial. Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}. Importantly, carelessly cloning code from one project and reusing it in another project can also cause software licensing conflict \cite{German2009}.

The rise of the Internet ignites tremendous amount of source code sharing online. This online code artefacts are very useful for software development and also valuable for educational purposes \cite{x}. Nonetheless, the process of sharing source code on the web is very similar to code cloning. On question-and-answer (Q\&A) websites such as Stackoverflow, most of the answers contain at least one code snippet showing how to solve a specific programming problem. The code snippet that is given as an example is usually copied from somewhere else. It can be cloned and modified from the question, copied from the answerer's own projects, or from other locations including open source software (OSS) systems.

In this study, we focus on a special type of code clones between software projects and Q\&A websites which we call ``online code clones''. There are three ways to create online code clones: 1) code is cloned from a software project to Q\&A website as an example; 2) code is cloned from Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; and 3) code is implicitly cloned from one software project to another by having Q\&A website as a medium. Online code clones can similarly lead to the problem of bug propagation as the classical code clones. However, they are harder to locate and fix since the search scope is no longer contained in a local repository. %Since reusing source code from Stackoverflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
This is an emerging and challenging problem to address and there is still limited studies in this area. %We are interested to gain more insights of online code clone in this study.

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used clone detection tools to discover 130,644,707 clone pairs and manually investigated 2,371 meaningful clone pairs between Java code fragments obtained from Stackoverflow accepted answers and 63 Java open source projects.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and online Q\&A websites:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which violate their software licenses. Furthermore, 30 out of the 48 clones are outdated and dangerous for being reused.

\section{Empirical Study}
We perform and empirical study of online code clones between Stackoverflow Java accepted answers and 63 Java open source projects.

The study aims to answer the following research questions: \\ 
\textbf{RQ1 (online code clone):} \textit{To what extent  source code is reused between Q\&A websites and open source projects?} We would like analyse quantitatively the number of online code clones between a Q\&A website, Stackoverflow, and open source projects. \newline
\textbf{RQ2 (flow of online code clone):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied. Is it from Q\&A websites to open source projects, or the other way around, or both? \newline
\textbf{RQ3 (classification of online code clone):} \textit{Are there any differences among online code clones?} We would like to classify and group them to gain insights of their common properties. \newline
\textbf{RQ4 (effects of online code clone):} \textit{Are online codes clone harmful?} Is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?

\subsection{Experimental Framework}
The experimental framework is depicted in Figure \ref{}. We deploy clone detection tools to locate clones between two locations: code snippets obtained from a Q\&A website, and open source projects. The clone report is pruned to contain only inter clone pairs between the two locations. All intra clone pairs within the Q\&A website and open source projects are removed. Clone pairs reported from the two clone detectors are matched to find agreements using Bellon's criteria \cite{Bellon2007}. This step generates \textbf{agreement-based clone pairs}. Next, clone pairs from each of the clone detection tools that do not agree with the other tool are ranked and selected. This step generates \textbf{non agreement-based clone pairs}. Agreement-based and non agreement-based clone pairs are looked at and classified manually.

Later, we compare licensing information of manually identified true positive clone pairs to see if they have any licensing conflicts. Moreover, we look forward through history of the clones from the projects' versioning systems to see if there is any changes made to the clones after it has been copied.

\subsection{Experimental Setup}
\subsubsection{Datasets}
\textbf{Stackoverflow}: we extracted 144,075 Java code snippets from accepted answers in a snapshot of Stackoverflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The data dump is in XML format containing information regarding Stackoverflow questions and answers and supporting data such as user accounts and timestamps. Code snippet is a piece of code located between \texttt{<code>} tags. These snippets are extracted from the XML dump using regular expressions. We then filtered the snippets with two filtering criteria. First, we ignore snippets that are less than 6 lines. Second, we are only interested in code snippets from answers that are marked as ``accepted'' since they have high chance to be reused.

\textbf{Qualitas corpus}: we selected the latest version of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects. \textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects. The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.

\subsubsection{Clone Detectors}
We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. There is a few restrictions in terms of choosing clone detection tools for this study. First, due to nature of code snippets posted on Stackoverflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets which are not in a complete block or compilable. This restriction forces us to remove two well-known clone detectors; CCFinder \cite{Kamiya2002}, and DECKARD \cite{Jiang2007a}; from our study since they failed to analyse the complete 144,075 Stackoverflow snippets. Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 63 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time. We found that both Simian and NiCad are able to handle clones in this situation with an acceptable running time.

\subsubsection{Agreement-based Clone Detection}
Since we did not have the clone oracle of the two datasets, we adopted an idea of clone agreement used in clone research \cite{Wang2013,Funaro2010} to help filtering the reported clones for manual investigation.
